Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
moved some sections to appendix

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing

$$
p_{ij} = \frac{w(t_i - t_j)}{\sum_{i \neq k} }
$$
## Results
[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

@@

[TK: Beta values]
Fitting our Bayesian model, which extends the method of Thompson et. al, values of beta were estimated for temperature, relative humidity, Gross Domestic Product (GDP) and population density, respectively.  Thus, our model estimates $\beta^T = [,,,,]$ in
$$ R_i(t) = \exp\left( \theta(t) + \lambda_i + \mathbf{\beta}^T x_i(t) + \varepsilon_i(t) \right)$$
Note that each feature's data is standardized to mean 0 and variance 1.

@@

- $\lambda$ is an adjustment to the model based on the location you're in.
### Climate-Independent Basic R, by Date

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot5.png}
\end{center}
- R_0 is high in early phases, with an early spike on February 27, potentially due to increased in testing, which captures cases before.
- Climate-independent means ignores local climates, and produces an aggregate result.

### Estimated R in Cities by Date

@@

- local, no longer climate independent.

- You want to minimize the value episilon.

>>>>

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing the likelihood that a person at timestep $i$ is infected by a person infected at timestep $j$, and summing the likelihood for each $j$ across all its infectees to compute the $R$ value at timestep $j$. This method is outlined in detail in Wallinga and Teunis (2004)[8].

## Results
[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

@@

[TK: Beta Values]
Fitting our Bayesian model, which extends the method of Thompson et. al, values of beta were estimated for temperature, relative humidity, Gross Domestic Product (GDP) and population density, respectively.  Thus, our model estimates $\beta^T = [,,,,]$ in
$$ R_i(t) = \exp\left( \theta(t) + \lambda_i + \mathbf{\beta}^T x_i(t) + \varepsilon_i(t) \right)$$
Note that each feature's data is standardized to mean 0 and variance 1.

@@

### Climate-Independent Basic R, by Date

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot5.png}
\end{center}

First, we observe that our computed value of $R_0$ in Italy matches what We observe that R_0 spikes in , with an early spike on February 27, potentially due to increased in testing, which captures cases before.

### Estimated R in Various Provinces

@@

Observe that in many cities, our estimated $R_0$ values are extremely high
